Future challenges for Research Software Engineering

### 2025-05-18 future_challenges_for_RSEng.tex
work in another comment

\begin{story}{New career paths}{New career paths}
Ken, though trained as a physicist, found his passion not in theory, but in keeping the quantum computers humming. He became the go-to expert for troubleshooting entangled qubits and stabilizing delicate cryogenic systems. His unique blend of physics knowledge and hands-on problem solving earned him a new title among his peers: the first Quantum RTP. In a world where theory meets reality, Ken quietly ensures the future of quantum computing stays on track.
\end{story}
\section{What is in this future for RSEs and where to go from here?}
%FG-NOTE: I think we can use this part to wrap things a bit up, and describe how this future then looks like.
%GC-NOTE: Shall we add another story box here? Ideas what we write here?
It is hard to conclude a piece written about the future, but we have tried to list some of the trends that we foresee.
The material presented here is based on the outputs of a workshop, but extended with the authors' ideas.
Nevertheless there are some things that we declared out of scope here.
Among that is the ongoing digital transformation in wider society.
Digital competencies in the general population continue to increase, making jumping to software development easier than before.
But this digitalisation will also lead to changes in the way societies interact and therefore will translate into changes in how academia perceives itself.
We have also not delved into the interaction with industry much.
There are also some trends that we believe will stay with us over the coming years.
The differentiation of job profiles in academia, that has started with profiles such as the RSE will continue.
Societies will be facing new questions, that arise from technologies such as generally available AI systems.

>>>>

\begin{story}{New career paths}{New career paths}
Ken, though trained as a physicist, found his passion not in theory, but in keeping the quantum computers humming. He became the go-to expert for troubleshooting entangled qubits and stabilizing delicate cryogenic systems. His unique blend of physics knowledge and hands-on problem solving earned him a new title among his peers: the first Quantum RTP. In a world where theory meets reality, Ken quietly ensures the future of quantum computing stays on track.
\end{story}
\section{What is in this future for RSEs?}
%FG-NOTE: I think we can use this part to wrap things a bit up, and describe how this future then looks like.
%GC-NOTE: Shall we add another story box here? Ideas what we write here?
In the previous sections, we have tried to list some of the trends that we foresee.
The material presented here is based on the outputs of a workshop, but extended with the authors' ideas.
Nevertheless there are some things that we declared out of scope here.
Among that is the ongoing digital transformation in wider society.
Digital competencies in the general population continue to increase, making jumping to software development easier than before.
But this digitalisation will also lead to changes in the way societies interact and therefore will translate into changes in how academia perceives itself.
We have also not delved into the interaction with industry much.
There are also some trends that we believe will stay with us over the coming years.
The differentiation of job profiles in academia, that has started with profiles such as the RSE will continue.
Societies will be facing new questions, that arise from technologies such as generally available AI systems.
